Using Stochastic Modeling to Predict Long Timescale Transport Behavior of Solutes in an H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane

### 2019-08-16 Ben_Manuscripts/stochastic_transport/Outline.tex
Outline updates and removing unnecessary files

  \section{Introduction}
  %BJC: obviously this section will get beefed up
  We need highly selective membranes in order to perform efficient separations.

  \noindent Amphiphilic molecules are capable of self-assembling into ordered nanostructures.

  Lytropic liquid crystals are a class of amphiphilic molecules that can be cross-linked
  into mechanically strong membranes.
  \begin{itemize}
  	\item H\textsubscript{II} phase lyotropic liquid crystals have densely packed, uniform
	sized pores and have the potential to disrupt conventional membrane separation
	techniques by being selective based not only on size and charge, but on chemical
	functionality as well.
	\item Q\textsubscript{I} phase LLCs consist of a tortuous network of 3D interconnected
	pores. They are easier to make.
  \end{itemize}

  We can only learn so much from experiment. MD can give us mechanistic insights with
  atomistic resolution so that we can intelligently design new membranes for 
  solute-specific separations.

  In our previous work, we studied the transport of 20 small polar molecules
  in an H\textsubscript{II} phase LLC membrane.
  \begin{itemize}
    \item In general, we observed subdiffusive transport behavior characterized 
    by intermittent hops separated by periods of entrapment.
    \item We identified three mechanisms responsible for the solute trapping behavior:
    entanglement among monomer tails, hydrogen bonding with monomer head groups, and
    association with sodium counter ions.
  \end{itemize}

  % BJC: I've been trying to understand the following justification a bit more. Does it
  % rely on the MSD becoming linear so we can get experimentally diffusion constants? Is
  % it just to try and reduce uncertainty in our MSD predictions? What can we learn from
  % long stochastic simulations that we can't learn from the shorter simulations.
  % BJC: To me the value in this is gaining a deeper mechanistic understanding by 
  % putting things in terms of easily interpreted equations.
  % BJC: Maybe it's just a combination of both.
  Unfortunately, the timescales that we can simulate with MD are insufficient to be
  able to make well-converged predictions of macroscopic transport properties 
  traditionally used to characterize membranes in the lab.

  One can draw from a number of scientific field to model transport behavior as a
  stochastic process.
  \begin{itemize}
    \item In the simulation literature, most start with mean squared displacement (MSD)
    \item Due to the time scales most people simulate, the MSD does not give a complete
    picture of what happens long-term.
    \item Markov state models are popular with researchers of proteins which have 
    many dynamical states occurring over multiple time scales.
    \item The anomalous diffusion literature 
    \item The financial literature studies a wide range of time series behavior which 
    may be particularly useful for describing short time scale dynamics.
  \end{itemize}

  % brief (1 paragraph) review of techniques for predicting long time scale behavior
  The are numerous ways one can approach modeling transport behavior, withing varying
  levels of complexity.
  \begin{itemize}
    \item Most

    \item Mean first passage time?

    \item Hidden markov models are useful for when states are known but one cannot
  \end{itemize}
  % Ornstein-Uhlenbeck (Gaussian + non-Gaussian)

  Talk about finance, single particle tracking and other places this type of analysis
  are used. Use word ubiquitous

  In this work, we explore three approaches to model the long timescale behavior
  of the four solutes fasted moving solutes studied in our previous work.
  \begin{itemize}
    \item Specifically, we study methanol, urea, ethylene glycol and acetic acid
  	\item Our first approach is based on the anomalous diffusion literature.
  	\item The second approach uses Markov state models (MSMs) 
  	\item The third uses an infinite hidden Markov model (iHMM), an unsupervised machine
  	learning algorithm which groups solute behavior into different dynamical states.
  	% BJC: somewhere emphasize that this last approach is powerful since it doesn't 
  	% require anything different in systems with more complex geometries (i.e. QI)
  \end{itemize}

@@

  We ran all MD simulations and energy minimizations using GROMACS 2018. We
  performed all post-simulation trajectory using python scripts which are available
  online at \texttt{https://github.com/shirtsgroup/LLC\_Membranes}.

@@

  We extended the 1 $\mu$s simulations of our previous work to 5 $\mu$s in order
  to collect ample data.
  \begin{itemize}
    \item We simulated the system with a time step of 2 fs at a pressure of 1 bar
    and 300 K controlled by the Parinello-Rahman barostat and the v-rescale thermostat
    respectively.
  \end{itemize}

@@

  A Markov state model decomposes a time series into a set of discrete states
  with transitions between states defined by a transition probability matrix, T,
  which describes the conditional probability of jumping to a specific 
  state given the previously observed state.~\cite{pande_everything_2010,wehmeyer_introduction_2018}
  \begin{itemize}
    \item In the context of molecular simulations, MSMs are frequently used
    to study systems with slow dynamics, such as protein folding.~\cite{snow_how_2005,chodera_automatic_2007}
    \item Researchers typically aim to come up with a low dimensional 
    representation of the system based on features which preserve the process
    kinetics. This facilitates the identification of discrete states from
    which T is generated.
    \item Software packages such as MSMbuilder~\cite{beauchamp_msmbuilder2:_2011}
    and pyEMMA~\cite{scherer_pyemma_2015} provide work flows capable 
    of featurization and dimensional reduction.
  \end{itemize}

  In this work, we define a total of 8 discrete states based on the 3 trapping
  mechanisms observed in our previous work. 
  \begin{itemize}
  	\item Therefore, there is no need to subject our trajectories to any reduction
  	in dimensionality. 
  	%BJC: not sure the best way to lay these out
  	\item The states we've chosen include all combinations of trapping mechanisms 
  	in the pore and out of the pore:
  	\begin{enumerate}
  	  \item Trapped in tails
  	  \item Trapped in tails and hydrogen bonding
  	  \item Trapped in tails and associated with sodium
  	  \item Trapped in tails, hydrogen bonding and associated
  	  \item In pores
  	  \item In pores and hydrogen bonding
  	  \item In pores and associated with sodium
  	  \item In pores, hydrogen bonding and associated
  	\end{enumerate}
  	\item These choices assume that there are no significant kinetic effects resulting
  	from solute conformational changes or pore size fluctuations, an assumption 
  	that may be relaxed in future work.
  	\item However, we will adopt the validation techniques used in the packages
  	mentioned above.  
  \end{itemize}

@@

  \noindent We recorded the $z$-direction displacement at each time step in order to construct
  individual emission distributions for each state and transition between states.
  \begin{itemize}
    \item While the dynamics of the states themselves are important, the 
    majority of observations involve transitions between states, so properly modeling
    the transition dynamics is even more important.
    %BJC: some of the transitions are pretty rare, so those emission distributions might be less reliable
    \item The shape of the distributions are symmetric and heavy-tailed. 
  \end{itemize}

@@

  L\'evy stable distributions often have heavy tails and an undefined variance 
  which can give rise to arbitrarily long particle displacements.
  \begin{itemize}
  	\item We do not observe hops longer than x nm in our simulations which 
  	emphasizes that these distributions are only an approximation.
    \item We avoid unrealistic, enormous hops problem by truncating the tails
    of the distribution. %BJC: can add some citations about truncated Levy distributions
    \item Since solutes in our system cannot hop further than the length of our 
    simulation unit cell, we truncate the tails of the distribution at this
    magnitude.
    % BJC: Is this actually the right way to do this? I am looking at unwrapped coordinates,
    % so theoretically a particle can move as far as it wants between frames.
    % BJC: The cut-off choice is pretty important and has a significant effect on MSD. 
    % For example, if I truncate at the unit cell length I reproducably get a final MSD of ~ 66 nm^2 (1000 ns stochastic simulation)
    % If I truncate the tails at double the unit cell length, I get a final MSD of ~107 nm^2
    % The uncertainty also increases (since variance diverges for these distributions)
    % So maybe it makes the most sense to truncate based on largest observed hops.
  \end{itemize}

  We simulated realizations of the stochastic process using the probability transition
  matrix and emission distributions.
  \begin{itemize}
    \item For each trajectory simulated, we chose an in initial state randomly from a 
    uniform distribution. %BJC: could construct initial distribution but I'm not sure how reliable that is based on 24 solutes that are started in the pore center. (need to chop off beginning 5 ns or so to get rid of that initial dependence)
    \item We randomly drew subsequent state transitions and corresponding emissions 
    from the rows of the probability transition matrix and the appropriate emission
    distribution respectively.
  \end{itemize}

@@

  For solutes in our system, the distribution of hop lengths appears to be
  well-represented by a Gaussian distribution.~\cite{metzler_random_2000,
  metzler_anomalous_2014,neusius_subdiffusion_2009}
  \begin{itemize}
	\item We are most interested in the standard deviation, $\sigma$, of the 
	hop length distribution.
  \end{itemize}

@@

@@

%  We calculated macroscopic diffusion coefficients by simulating trajectories orders of
%  magnitude longer than our molecular simulations.
  \noindent For each solute, we simulated 10000 5 $\mu$s sFBM trajectories. 
  \begin{itemize}
	\item We constructed trajectories by simulating	sequences of dwell times and correlated 
	hop	lengths generated based on parameters randomly chosen from our bootstrapped parameter
	distributions.
	\item We propagated each trajectory until the total time reached 1 $\mu$s, and truncated
	the last data point so that the total time exactly equaled 5 $\mu$s. 
    \item Valid comparisons are only possible between fixed length sFBM simulations. The
    power law dwell time behavior gives rise to the aging phenomenon, embodied by
    a decrease in MSD with measurement time.~\cite{neusius_subdiffusion_2008,metzler_anomalous_2014}
    \item We reported the MSD after 5 $\mu$s with corresponding 95 \% intervals
% Following probably better suited for supporting information, if included at all
%	\item We randomly sample Gaussian hop lengths using the
%	\texttt{numpy.random.normal} method of the \texttt{numpy} python package.
%	\item We randomly sampled dwell times from a discrete power law
%	distribution based on the recommendations of Clauset et
%	al.~\cite{clauset_power-law_2009}: 
%	\begin{equation}
%	x = \lfloor
%	(x_{min} - \tfrac{1}{2})(1 - r)^{-1/(\alpha - 1)} + \tfrac{1}{2} \rfloor
%	\label{eqn:discrete_powerlaw_draws}
%	\end{equation}
%	where $r$ is randomly drawn from a uniform distribution which we simulated
%	with \texttt{numpy.random.uniform}.
%	\item We found that thermal noise does not significantly influence the MSD and
%	therefore did not add any noise to the simulated trajectories. (See supporting info)
  \end{itemize}

@@

%  \subsubsection*{Coordination number}

%  We quantified the coordination of solutes with surrounding molecules.
%  \begin{itemize}
%  	\item For each frame, we counted the identities and number of
%  	coordinated molecules to a given solute based on a distance cut-off. 
%	\item We found that this approach is more useful than calculating the
%	3D spherical radial distribution function because it gives detailed
%	frame-by-frame information rather than an average. 
%  \end{itemize}

  \subsection{The Infinite State Hidden Markov Model}\label{method:iHMM}  %BJC: potentially a separate paper

  Hidden Markov models (HMMs) are a useful and widely used technique
  for modeling sequences of observations where the probability of the next observation
  in a sequence depends only on a previous unobserved, or hidden, state.~\cite{beal_infinite_2002}
  \begin{itemize}
    \item In the context of our simulations, the observations correspond to 
    the center of mass coordinates of the solutes versus time, and the states
    correspond to the dynamical behavior which give rise to those types
    of observations.
    \item Unfortunately, standard HMMs require the number of hidden states to be known
    a priori.
  \end{itemize}

  The infinite-state HMM overcomes this drawback by placing a hierarchical
  Dirichlet process (HDP) prior on the transition probabilities.
  \begin{itemize}
    \item Using some base probability distribution, H, a Dirichlet process 
    (DP) generates distributions over a countably infinite number of 
    probability measures:
    \begin{equation}
      G_0 = \sum_{k=1}^{\infty} \beta_k \delta_{\theta_k} ~~ \theta_k \sim H, \beta \sim GEM(\gamma)
    \end{equation}
    where the $\theta_k$ are values drawn from the base distribution and the
    weights $\beta_k$ come from a stick-breaking process parameterized by the concentration 
    parameter $\gamma$ (equivalently referred to as GEM($\gamma$)). 
    \item The concentration parameter expresses one's confidence in H relative to the posterior 
    and is closely related to the number of data observations.
    \item Each row, $G_j$, of the transition matrix is produced by drawing from a DP specified 
    using the $\beta$ vector as a discrete base distribution and a separate concentration
    parameter, $\alpha$.
    \begin{equation}
      G_j = \sum_{k=1}^{\infty} \pi_{jk} \delta_{\theta_k} ~~ \pi_j \sim DP(\alpha, \beta)
    \end{equation}
    \item This hierarchical specification ensures that the transition probabilities in 
    each row share the same support points \{$\theta_1$, ..., $\theta_k$\}.
  \end{itemize}

@@

  Solute motion is influenced by the same three trapping mechanisms observed in our
  previous works.
  \begin{itemize}
    \item The extent to which each trapping mechanism influences each solute is
  depicted graphically in Figure TBD.
    \item Same types of figures from transport paper:
    \item Fraction participating in hydrogen bonds, fraction associated, fraction
    in the tails.
    \item Lifetimes of hbonds and sodium associations?
  \end{itemize}

@@

  \begin{figure}[!h]
  \includegraphics[width=\textwidth]{MET_msd.pdf}
  \caption{}\label{fig:msd_MET}
  \end{figure}

  Anti-correlation between hops may be responsible for subdiffusive behavior.
  \begin{itemize}
    \item In general, we observe negative correlation between hops.
    \item A L\'evy driven OU process may be a more appropriate way to model
    the stochastic dynamics of this system since you can incorporate autocorrelation.
    \item Extracting reliable correlation functions is difficult with our data
    due to relatively frequent switching resulting in sets of short disjoint time 
    series describing each state.
    \item Therefore we did not do this and attempted to fit a different model. 
    %BJC: we could add some artificial correlation to test the anti-correlation hypothesis
  \end{itemize}

@@

  Using the techniques from Section~\ref{section:model_sFBM}, we extracted values 
  of $\sigma$, $\alpha$ and $H$ for each solute for the 1 and 2 mode model 
  (see Table~\ref{table:sfbm_params}).
  \begin{itemize}
    \item In most cases, it is easy to relate $\sigma$, $\alpha$ and $H$ to the
    simulated MSD values presented in Table~\ref{table:simulations}. 
  	\item Higher values of $\sigma$ indicate larger average hop lengths.
  	\item Higher values of $\alpha$ mean that there will be less sampling of 
  	long dwell times.
  	\item Values of $H$ near the Brownian limit of 0.5, indicate a lower degree
  	of anti-correlation.
  	\item All of which contribute to an overall increase in the MSD.
  \end{itemize}

  % BJC: worth including single parameter model (i.e. no radial dependence) to 
  % show its shortcomings? Or send to supporting information
  % BJC: obviously still needs 2 mode data
  \begin{table}[h]
  \centering
  \begin{tabular}{cccc}
  \toprule
  System & $\sigma$ ($nm$) & $\alpha$ & $H$ \\
  \midrule
  Methanol & 0.46 & 0.85 & 0.40 \\
  Urea & 0.33 & 0.64 & 0.40 \\
  Ethylene Glycol & 0.35 & 0.64 & 0.36 \\
  Acetic Acid & 0.28 & 0.51 & 0.44 \\
  \bottomrule
  \end{tabular}
  \caption{We calculated values $\sigma$, $\alpha$ and $H$ from MD simulation
  trajectories and then computed the average ensemble-averaged MSD of 10000 
  simulated trajectories.}\label{table:sfbm_params}
  \end{table}

  \noindent We compared the MSD of simulated sFBM trajectories to MD simulated
  MSDs.
  \begin{itemize}
	\item We simulated 10000 sFBM trajectories of the same length as our MD
	simulations, as described in Section~\ref{section:model_sFBM} of the Methods.
	\item The final MSDs of the sFBM trajectories are compared to those 
	calculated directly from MD simulations in Figure~\ref{fig:all_msds}. 
	\item We would like to emphasize that we rely on the MD MSD values in order to
	define trends in the total MSD, while the sFBM trajectories and parameter 
	values allow us to speculate as to the reasons for the observed trends. 
	\item There is a non-negligible amount of error in the calculation of 
	each parameter which prevents us from reliably portraying our sFBM MSDs as
	reduced	uncertainty MD MSDs.
	% BJC: I think it's more the power law tails that increases uncertainty.
  \end{itemize}

>>>>

  \section{Introduction}
  %BJC: obviously this section will get beefed up
  We need highly selective membranes in order to perform efficient separations. \\

  \noindent Amphiphilic molecules are capable of self-assembling into ordered nanostructures.\\

  Lyotropic liquid crystals are a class of amphiphilic molecules that can be cross-linked
  into mechanically strong membranes.
  \begin{itemize}
  	\item H\textsubscript{II} phase lyotropic liquid crystals have densely packed, uniform
	sized pores and have the potential to disrupt conventional membrane separation
	techniques by being selective based not only on size and charge, but on chemical
	functionality as well.
	\item Q\textsubscript{I} phase LLCs consist of a tortuous network of 3D interconnected
	pores. They are easier to make.
  \end{itemize}

  We can only learn so much from experiment. MD can give us mechanistic insights with
  atomistic resolution so that we can intelligently design new membranes for 
  solute-specific separations.\\

  \noindent In our previous work, we studied the transport of 20 small polar molecules
  in an H\textsubscript{II} phase LLC membrane.
  \begin{itemize}
    \item In general, we observed subdiffusive transport behavior characterized 
    by intermittent hops separated by periods of entrapment.
    \item We identified three mechanisms responsible for the solute trapping behavior:
    entanglement among monomer tails, hydrogen bonding with monomer head groups, and
    association with sodium counter ions.
  \end{itemize}

  % BJC: I've been trying to understand the following justification a bit more. Does it
  % rely on the MSD becoming linear so we can get experimentally diffusion constants? Is
  % it just to try and reduce uncertainty in our MSD predictions? What can we learn from
  % long stochastic simulations that we can't learn from the shorter simulations.
  % BJC: To me the value in this is gaining a deeper mechanistic understanding by 
  % putting things in terms of easily interpreted equations.
  % BJC: Maybe it's just a combination of both.
  Unfortunately, the timescales that we can simulate with MD are insufficient to be
  able to make well-converged predictions of macroscopic transport properties 
  traditionally used to characterize membranes in the lab. \\

  One can project long timescale solute behavior by modeling transport as a
  stochastic process.
  \begin{itemize}
    \item Various disciplines study this type of problem in a number of ways.
    \item In the simulation literature, most start by measuring mean squared 
    displacement (MSD), as we did previously.  % This doesn't quite fit the thesis
    \item Due to the short time scales most people can feasibly simulate, the MSD 
    does not give a complete picture of what happens long-term, other than hinting
    at types of mechanisms that could lead to the curve's shape.
    \item mean first passage time?
    \item Markov state models are popular with researchers of proteins which have 
    many dynamical states occurring over multiple time scales.
    \item The anomalous diffusion literature explains the shape of MSD curves based
    on rigorous mathematical representations of transport mechanisms. This field is
    heavily used in analysis of single particle tracking experiments.
    \item Finally, the financial literature tackles similar problems from a more 
    general time series perspective. Their primary focus is towards predictions of
    stock market returns and volatility but their methods are widely applicable to
    modeling time series that exhibit a range of behavior.
  \end{itemize}

  In this work, we explore two approaches to model the long timescale behavior
  of the four solutes fasted moving solutes studied in our previous work.
  \begin{itemize}
    \item Specifically, we study methanol, urea, ethylene glycol and acetic acid
  	\item Our first approach uses Markov state models (MSMs) 
  	\item The second approach is based on the anomalous diffusion literature.
%  	\item The third uses an infinite hidden Markov model (iHMM), an unsupervised machine
%  	learning algorithm which groups solute behavior into different dynamical states.
  	% BJC: somewhere emphasize that this last approach is powerful since it doesn't 
  	% require anything different in systems with more complex geometries (i.e. QI)
  \end{itemize}

@@

  We ran all MD simulations and energy minimizations using GROMACS 2018. We  % needs gromacs citations
  performed all post-simulation trajectory using python scripts which are available
  online at \\ \texttt{https://github.com/shirtsgroup/LLC\_Membranes}.

@@

  \noindent We extended the 1 $\mu$s simulations of our previous work to 5 $\mu$s in order
  to collect ample data.
  \begin{itemize}
    \item We simulated the system with a time step of 2 fs at a pressure of 1 bar
    and 300 K controlled by the Parinello-Rahman barostat and the v-rescale thermostat
    respectively.
    \item We recorded frames every 0.5 ns
  \end{itemize}

@@

  A Markov state model (MSM) decomposes a time series into a set of discrete states
  with transitions between states defined by a transition probability matrix, T,
  which describes the conditional probability of jumping to a specific 
  state given the previously observed state.~\cite{pande_everything_2010,wehmeyer_introduction_2018}
  \begin{itemize}
    \item In the context of molecular simulations, MSMs are frequently used
    to study systems with slow dynamics, such as protein folding.~\cite{snow_how_2005,chodera_automatic_2007} % might move to intro
    \item Researchers typically aim to come up with a low dimensional 
    representation of the system based on features which preserve the process
    kinetics. This facilitates the identification of discrete states from
    which T is generated.
    \item Software packages such as MSMbuilder~\cite{beauchamp_msmbuilder2:_2011}
    and pyEMMA~\cite{scherer_pyemma_2015} provide work flows capable 
    of featurization and dimensional reduction.
  \end{itemize}

  In this work, we define a total of 8 discrete states based on the 3 trapping
  mechanisms observed in our previous work. 
  \begin{itemize}
  	\item Therefore, there is no need to subject our trajectories to any reduction
  	in dimensionality. 
  	\item However, we will adopt the validation techniques used in the packages
  	mentioned above.  
  	%BJC: not sure the best way to lay these out
  	\item The states we've chosen include all combinations of trapping mechanisms 
  	in the pore and out of the pore:
  	\begin{enumerate}
  	  \item Trapped in tails
  	  \item Trapped in tails and hydrogen bonding
  	  \item Trapped in tails and associated with sodium
  	  \item Trapped in tails, hydrogen bonding and associated
  	  \item In pores
  	  \item In pores and hydrogen bonding
  	  \item In pores and associated with sodium
  	  \item In pores, hydrogen bonding and associated
  	\end{enumerate}
  	\item These choices assume that there are no significant kinetic effects resulting
  	from solute conformational changes or pore size fluctuations, an assumption 
  	that may be relaxed in future work.
  \end{itemize}

@@

  \noindent We recorded the $z$-direction displacement at each time step in order to construct
  individual emission distributions for each state and transition between states.
  \begin{itemize}
    \item While the dynamics of the states themselves are important, the 
    majority of observations involve transitions between states, so properly modeling
    the transition dynamics is even more important.
    \item This results in 64 distinct emission distributions. Some are far more
    populated than others. % BJC: not sure if the emission distributions are reversible. i.e. if 1 --> 2 transition has same emission distribution as 2 --> 1. It might be required to be Markovian since transition matrix is symmetric. Not sure.
    %\item The shape of the distributions are symmetric and heavy-tailed. 
  \end{itemize}

@@

  L\'evy stable distributions often have heavy tails and an undefined variance 
  which can give rise to arbitrarily long particle displacements.
  \begin{itemize}
  	\item We do not observe hops longer than x nm in our simulations which 
  	emphasizes that these distributions are only an approximation.
    \item We avoid enormous and unrealistic hops problem by truncating the tails
    of the distribution. %BJC: can add some citations about truncated Levy distributions
    \item Since solutes in our system cannot hop further than the length of our 
    simulation unit cell, we truncate the tails of the distribution at this
    magnitude.
    % BJC: Is this actually the right way to do this? I am looking at unwrapped coordinates,
    % so theoretically a particle can move as far as it wants between frames.
    % BJC: The cut-off choice is pretty important and has a significant effect on MSD. 
    % For example, if I truncate at the unit cell length I reproducably get a final MSD of ~ 66 nm^2 (1000 ns stochastic simulation)
    % If I truncate the tails at double the unit cell length, I get a final MSD of ~107 nm^2
    % The uncertainty also increases (since variance diverges for these distributions)
    % So maybe it makes the most sense to truncate based on largest observed hops.
  \end{itemize}

  We simulated realizations of the stochastic process using the probability transition
  matrix and emission distributions.
  \begin{itemize}
    \item For each trajectory simulated, we chose an initial state randomly from a 
    uniform distribution. %BJC: could construct initial distribution but I'm not sure how reliable that is based on 24 solutes that are started in the pore center. (need to chop off beginning 5 ns or so to get rid of that initial dependence)
    \item We randomly drew subsequent state transitions and corresponding emissions 
    from the rows of the probability transition matrix and the appropriate emission
    distribution respectively.
  \end{itemize}

@@

  For solutes in our system, the distribution of hop lengths appears to be
  well-represented by a Gaussian distribution.~\cite{metzler_random_2000,
  metzler_anomalous_2014,neusius_subdiffusion_2009}  % Note that this is different from the distribution of all increments (which is heavy-tailed)
  \begin{itemize}
	\item We are most interested in the standard deviation, $\sigma$, of the 
	hop length distribution.
  \end{itemize}

@@

  For the two mode model, we needed to define a probability transition matrix 
  describing transitions between the tail and pore region.

@@

%  We calculated macroscopic diffusion coefficients by simulating trajectories orders of
%  magnitude longer than our molecular simulations.
  \noindent For each solute, we simulated 10000 5 $\mu$s sFBM trajectories. 
  \begin{itemize}
	\item We constructed trajectories by simulating	sequences of dwell times and correlated 
	hop	lengths generated based on parameters randomly chosen from our bootstrapped parameter
	distributions.
	\item We propagated each trajectory until the total time equaled or exceeded 5 $\mu$s, 
	then truncated the last data point so that the total time exactly equaled 5 $\mu$s. 
    \item Valid comparisons are only possible between fixed length sFBM simulations. The
    power law dwell time behavior gives rise to the aging phenomenon, embodied by
    a decrease in MSD with measurement time.~\cite{neusius_subdiffusion_2008,metzler_anomalous_2014}
    \item We reported the MSD after 5 $\mu$s with corresponding 95 \% intervals
% Following probably better suited for supporting information, if included at all
%	\item We randomly sample Gaussian hop lengths using the
%	\texttt{numpy.random.normal} method of the \texttt{numpy} python package.
%	\item We randomly sampled dwell times from a discrete power law
%	distribution based on the recommendations of Clauset et
%	al.~\cite{clauset_power-law_2009}: 
%	\begin{equation}
%	x = \lfloor
%	(x_{min} - \tfrac{1}{2})(1 - r)^{-1/(\alpha - 1)} + \tfrac{1}{2} \rfloor
%	\label{eqn:discrete_powerlaw_draws}
%	\end{equation}
%	where $r$ is randomly drawn from a uniform distribution which we simulated
%	with \texttt{numpy.random.uniform}.
%	\item We found that thermal noise does not significantly influence the MSD and
%	therefore did not add any noise to the simulated trajectories. (See supporting info)
  \end{itemize}

@@

  % BJC: can ignore this section for now. 
  \subsection{The Infinite State Hidden Markov Model}\label{method:iHMM}  %BJC: potentially a separate paper

  Hidden Markov models (HMMs) are a useful and widely used technique
  for modeling sequences of observations where the probability of the next observation
  in a sequence depends only on a previous unobserved, or hidden, state.~\cite{beal_infinite_2002}
  \begin{itemize}
    \item In the context of our simulations, the observations correspond to 
    the center of mass coordinates of the solutes versus time, and the states
    correspond to the dynamical behavior which give rise to those types
    of observations.
    \item Unfortunately, standard HMMs require the number of hidden states to be known
    a priori.
    \item One can partially overcome this by testing a range of numbers of 
    hidden states and determining which is the best representation of their
    data.
  \end{itemize}

  The infinite-state HMM overcomes this drawback by placing a hierarchical
  Dirichlet process (HDP) prior on the transition probabilities.
  \begin{itemize}
    \item Using some base probability distribution, H, a Dirichlet process 
    (DP) generates distributions over a countably infinite number of 
    probability measures:
    \begin{equation}
      G_0 = \sum_{k=1}^{\infty} \beta_k \delta_{\theta_k} ~~ \theta_k \sim H, \beta \sim GEM(\gamma)
    \end{equation}
    where the $\theta_k$ are values drawn from the base distribution and the
    weights $\beta_k$ come from a stick-breaking process parameterized by the concentration 
    parameter $\gamma$ (equivalently referred to as GEM($\gamma$)). 
    \item The concentration parameter expresses one's confidence in H relative to the posterior 
    and is closely related to the number of data observations.
    \item Each row, $G_j$, of the transition matrix is produced by drawing from a DP specified 
    using the $\beta$ vector as a discrete base distribution and a separate concentration
    parameter, $\alpha$.
    \begin{equation}
      G_j = \sum_{k=1}^{\infty} \pi_{jk} \delta_{\theta_k} ~~ \pi_j \sim DP(\alpha, \beta)
    \end{equation}
    \item This hierarchical specification ensures that the transition probabilities in 
    each row share the same support points \{$\theta_1$, ..., $\theta_k$\}.
    \item Once the model has converged only a finite number of states will have significant
    sampling.
  \end{itemize}

@@

  \noindent Solute motion is influenced by the same three trapping mechanisms observed in our
  previous work.
  \begin{itemize} 
    \item The extent to which each trapping mechanism influences each solute is
  	depicted graphically in Figure TBD.
    \item Same types of figures from transport paper:
    \item Fraction participating in hydrogen bonds, fraction associated, fraction
    in the tails.
    \item Lifetimes of hbonds and sodium associations?
  \end{itemize}

@@

  \begin{figure}[!h]
  \centering
  \includegraphics[width=0.5\textwidth]{MET_msd.pdf}
  \caption{}\label{fig:msd_MET}
  \end{figure}

  \noindent Anti-correlation between hops may be responsible for subdiffusive behavior.
  \begin{itemize}
    \item In general, we observe negative correlation between hops.
    \item A L\'evy driven OU process may be a more appropriate way to model
    the stochastic dynamics of this system since you can incorporate autocorrelation.
    \item Extracting reliable correlation functions is difficult with our data
    due to relatively frequent switching resulting in sets of short disjoint time 
    series describing each state.
    \item Therefore we did not do this and attempted to fit a different model. 
    %BJC: we could add some artificial correlation to prove the anti-correlation hypothesis
  \end{itemize}

@@

  Using the techniques from Section~\ref{method:model_sFBM}, we extracted values 
  of $\sigma$, $\alpha$ and $H$ for each solute for the 1 and 2 mode model 
  (see Table~\ref{table:sfbm_params}).
  \begin{itemize}
    \item In most cases, it is easy to relate the values of $\sigma$, $\alpha$ 
    and $H$ presented in Table~\ref{table:sfbm_params} to the simulated MSD values . 
  	\item Higher values of $\sigma$ indicate larger average hop lengths.
  	\item Higher values of $\alpha$ mean that there will be less sampling of 
  	long dwell times.
  	\item Values of $H$ near the Brownian limit of 0.5, indicate a lower degree
  	of anti-correlation.
  	\item All of which contribute to an overall increase in the MSD.
  \end{itemize}

  % BJC: worth including single parameter model (i.e. no radial dependence) to 
  % show its shortcomings? Or send to supporting information
  % BJC: obviously still needs 2 mode data
  % BJC: this is 1 microsecond data
  \begin{table}[h]
  \centering
  \begin{tabular}{cccc}
  \toprule
  System & $\sigma$ ($nm$) & $\alpha$ & $H$ \\
  \midrule
  Methanol & 0.46 & 0.85 & 0.40 \\
  Urea & 0.33 & 0.64 & 0.40 \\
  Ethylene Glycol & 0.35 & 0.64 & 0.36 \\
  Acetic Acid & 0.28 & 0.51 & 0.44 \\
  \bottomrule
  \end{tabular}
  \caption{We calculated values $\sigma$, $\alpha$ and $H$ from MD simulation
  trajectories and then computed the average ensemble-averaged MSD of 10000 
  simulated trajectories.}\label{table:sfbm_params}
  \end{table}

  \noindent We compared the MSD of simulated sFBM trajectories to MD simulated
  MSDs.
  \begin{itemize}
	\item We simulated 10000 sFBM trajectories of the same length as our MD
	simulations, as described in Section~\ref{method:model_sFBM} of the Methods.
	\item The final MSDs of the sFBM trajectories are compared to those 
	calculated directly from MD simulations in Figure~\ref{fig:all_msds}. 
	\item We would like to emphasize that we rely on the MD MSD values in order to
	define trends in the total MSD, while the sFBM trajectories and parameter 
	values allow us to speculate as to the reasons for the observed trends. 
	\item There is a non-negligible amount of error in the calculation of 
	each parameter which prevents us from reliably portraying our sFBM MSDs as
	reduced	uncertainty MD MSDs.
	% BJC: I think it's more the power law tails that increases uncertainty.
  \end{itemize}
